PMH3 - Functional Analysis

### 2013-01-06 PMH3 - Functional Analysis/PMH3 Lecture Notes.tex
Unified title naming
Changed author on PMH3
Added ToC to all notes
Changed tabs to spaces

\documentclass[10pt, reqno, oneside]{amsart}
\usepackage{amsthm, amsmath, amssymb}
\usepackage{setspace, graphicx, enumerate}
\onehalfspacing
% \usepackage{mathspec}
% \setallmainfonts{Minion Pro}

\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}

% \setlength{\columnsep}{50pt}
% \setlength{\columnseprule}{2pt}
% \setromanfont[Mapping=tex-text,Contextuals=w {NoWordInitial,NoWordFinal,NoLineInitial,NoLineFinal}]{Adobe Caslon Pro}
%\setsansfont[Scale=MatchLowercase,Mapping=tex-text]{Hoefler Text}
%\setmonofont[Scale=MatchLowercase]{Andale Mono}

@@

\title{PMH3 - Functional Analysis \\ Lecture Notes}								% Document Title
\author{James Parkinson}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle

@@

\begin{thm}[Projection]
	Let $(\Hil, \langle \cdot, \cdot, \rangle )$ be a Hilbert space.  Let $M \subseteq \Hil$ be closed and convex.  Let $x \in \Hil$.  THen there exists a unique point $m_x \in M$ which is closest to $x$, i.e. \[
		\| x - m_x \| = \inf_{m \in M} \| x - m \| = d
 	\]  
\end{thm}

@@

	Let \[ 
	\mathcal A_\R = \{ f \in \mathcal A \given \text{$f$ is real valued} \}. 
	\]  THen $\mathcal A_\R$ is an $\R$-subalgebra of $\mathcal C_\R(X)$.  It is unital, as $1 \in \mathcal A$ and it is real valued.

@@

	$(b) \Rightarrow (a)$.  Suppose $(b)$ holds.  Let $B_1 \subseteq X$ be bounded.  THen $B_1 \subseteq \alpha B$ for some $\alpha > 0$.  So \[
		\overline{T(B)} \subseteq \overline{T(\alpha B)} = \alpha \overline{T(B)}
	\] which is a closed subset of a compact set, and hence compact.

@@

\begin{lem}[Riesz's Lemma]
	Let $X$ be a normed vector space.  Let $Y \subsetneq X$ be a proper \textbf{closed} subspace.  Let $\theta \in (0, 1)$ be given. THen there exists $x$ with $\| x \| = 1$ such that $\| x - y \| \geq \theta$ for all $y \in Y$.  
\end{lem}
\begin{proof}
	Pick any $z \in X \backslash Y$.  Let $\alpha = \inf_{y \in Y} \| z - y \| > 0$ since $Y$ is closed.  Then by the definition of the infimum, there is $y_0 \in Y$ with $\alpha \leq \| z - y_0 \| \leq \frac{\alpha}{\theta}$.  Now let $x = \frac{x - y_0}{\| z - y_0 \|}$.  Then $\| x \| = 1$.

	Now, \begin{align*}
		\| x - y \| &= \left \| \frac{z - y_0}{\| z - y_0 \|} - y \right \| \\
					&= \frac{1}{\| z - y_0 \|} \left \| z - y_- + \| z - y_0 \| y \right \| \\
					&\geq \frac{\theta}{\alpha} \alpha = \theta
	\end{align*}
\end{proof}

@@

We now show $T x'_n$ is Cauchy, and hence converges.  We have \begin{align*}
	\| Tx'_m - T x'_n \| \leq \| T x'_m - T_k x'_m \| + \| T_K x'_m - T_k x'_n \| + T_k x'_n - T x'_n \|
\end{align*} where $k$ is to be chosen.  Suppose $\| x_n \| \leq M$ for all $n \geq 1$.  THen \begin{align*}
	\| Tx'_m - T x'_n \| \leq 2 M \| T - T_k \| + \| T_k x'+m - T_k x'_n \|
\end{align*} Let $\epsilon > 0$ be given. Since $\| T - T_k \| \rightarrow 0$ as $ k \rightarrow \infty$, fix a $k$ for which $\| T - T_k \| \leq \frac{\epsilon}{3M}$.  For this fixed $k$, we know $(T_k x'_n)$ converges, and so is Cauchy.  So there exists $N < 0$ such that $\| T_k x'm - T_k x'_n\| < frac{\epsilon}{3}$ for all $m,n < N$.  Hence $\|T x'_m - Tx'_n \| \leq \frac{2M}{\epsilon}{3M} + \frac{\epsilon}{3} = \epsilon$ for all $m , n > N$, so is Cauchy, and so converges. 
\end{proof}

>>>>

\documentclass[10pt, oneside, reqno]{amsart}
\usepackage{geometry, setspace, graphicx, enumerate, amssymb}
\onehalfspacing                 
\usepackage{fontspec,xltxtra,xunicode}
\defaultfontfeatures{Mapping=tex-text}

@@

\title{PMH3 - Functional Analysis}                              % Document Title
\author{Andrew Tulloch}
%\date{}                                           % Activate to display a given date or no date

\begin{document}
\maketitle \tableofcontents \clearpage

@@

\begin{thm}[Projection]
    Let $(\Hil, \langle \cdot, \cdot, \rangle )$ be a Hilbert space.  Let $M \subseteq \Hil$ be closed and convex.  Let $x \in \Hil$.  Then there exists a unique point $m_x \in M$ which is closest to $x$, i.e. \[
        \| x - m_x \| = \inf_{m \in M} \| x - m \| = d
    \]  
\end{thm}

@@

    Let \[ 
    \mathcal A_\R = \{ f \in \mathcal A \given \text{$f$ is real valued} \}. 
    \]  Then $\mathcal A_\R$ is an $\R$-subalgebra of $\mathcal C_\R(X)$.  It is unital, as $1 \in \mathcal A$ and it is real valued.

@@

    $(b) \Rightarrow (a)$.  Suppose $(b)$ holds.  Let $B_1 \subseteq X$ be bounded.  Then $B_1 \subseteq \alpha B$ for some $\alpha > 0$.  So \[
        \overline{T(B)} \subseteq \overline{T(\alpha B)} = \alpha \overline{T(B)}
    \] which is a closed subset of a compact set, and hence compact.

@@

\begin{lem}[Riesz's Lemma]
    Let $X$ be a normed vector space.  Let $Y \subsetneq X$ be a proper \textbf{closed} subspace.  Let $\theta \in (0, 1)$ be given. Then there exists $x$ with $\| x \| = 1$ such that $\| x - y \| \geq \theta$ for all $y \in Y$.  
\end{lem}
\begin{proof}
    Pick any $z \in X \backslash Y$.  Let $\alpha = \inf_{y \in Y} \| z - y \| > 0$ since $Y$ is closed.  Then by the definition of the infimum, there is $y_0 \in Y$ with $\alpha \leq \| z - y_0 \| \leq \frac{\alpha}{\theta}$.  Now let $x = \frac{z - y_0}{\| z - y_0 \|}$.  Then $\| x \| = 1$.

    Now, \begin{align*}
        \| x - y \| &= \left \| \frac{z - y_0}{\| z - y_0 \|} - y \right \| \\
                    &= \frac{1}{\| z - y_0 \|} \left \| z - y_0 + \| z - y_0 \| y \right \| \\
                    &\geq \frac{\theta}{\alpha} \alpha = \theta
    \end{align*}
\end{proof}

@@

We now show $T x'_n$ is Cauchy, and hence converges.  We have \begin{align*}
    \| Tx'_m - T x'_n \| \leq \| T x'_m - T_k x'_m \| + \| T_K x'_m - T_k x'_n \| + T_k x'_n - T x'_n \|
\end{align*} where $k$ is to be chosen.  Suppose $\| x_n \| \leq M$ for all $n \geq 1$.  Then \begin{align*}
    \| Tx'_m - T x'_n \| \leq 2 M \| T - T_k \| + \| T_k x'+m - T_k x'_n \|
\end{align*} Let $\epsilon > 0$ be given. Since $\| T - T_k \| \rightarrow 0$ as $ k \rightarrow \infty$, fix a $k$ for which $\| T - T_k \| \leq \frac{\epsilon}{3M}$.  For this fixed $k$, we know $(T_k x'_n)$ converges, and so is Cauchy.  So there exists $N < 0$ such that $\| T_k x'm - T_k x'_n\| < frac{\epsilon}{3}$ for all $m,n < N$.  Hence $\|T x'_m - Tx'_n \| \leq \frac{2M}{\epsilon}{3M} + \frac{\epsilon}{3} = \epsilon$ for all $m , n > N$, so is Cauchy, and so converges. 
\end{proof}
